\documentclass[aspectratio=1610]{beamer}

\usetheme{Hannover}
\usecolortheme{rose}
\definecolor{JagBlue}{HTML}{00205B}
\definecolor{JagRed}{HTML}{BF0D3E}

\usepackage{tikz,pgfplots,multicol}

%Center frame titles
\setbeamertemplate{frametitle}[default][center]

\title{Linear Algebra}

\date{Spring 2020}


\begin{document}



\begin{frame}\frametitle{Class norms (Section 101)}
On the first day of class, we agreed that we should all...
\begin{multicols}{2}
\begin{itemize}
\item Actually show up  and participate
\item Communicate well
\item Be flexible
\item Be prepared for class
\item Be helpful 
\item Be respectful of each other
\item Hold each other accountable
\item Do our best
\item Meet outside of class when needed
\item Ask questions
\item Do what is necessary
\end{itemize}
\end{multicols}

\vfill
Which of these has your team done well? Which of these does your team need to work at?
\end{frame}


\begin{frame}\frametitle{Class norms (Section 102)}
On the first day of class, we agreed that we should all...
\begin{multicols}{2}
\begin{itemize}
\item Be considerate and respectful of each other
\item Participate
\item Be punctual
\item Have a good work ethic
\item Be willing to help
\item Be willing to speak up
\item Be patient
\item Be quiet when needed
\item Attack problems, not people
\end{itemize}
\end{multicols}

\vfill
Which of these has your team done well? Which of these does your team need to work at?
\end{frame}

\begin{frame}\frametitle{Class norms (Section 103)}
On the first day of class, we agreed that we should all...
\begin{multicols}{2}
\begin{itemize}
\item Be patient
\item Pace ourselves
\item Be mindful of each other
\item Be civil
\item Contribute equal shares
\item Attend class
\item Be prepared for class
\item Not be afraid to make mistakes (and not judge others' mistakes)
\item Be accountable
\item Help keep each other afloat
\end{itemize}
\end{multicols}

\vfill
Which of these has your team done well? Which of these does your team need to work at?
\end{frame}


\begin{frame}\frametitle{Team assets}
Look over the list of assets your team compiled on the first day of class.
\vfill
\pause
For each team member, list one more asset. How has each team member helped the team so far this semester?
\vfill
\pause
You previously listed an area of improvement for each team member. Discuss how each of you is progressing in that area.

\end{frame}





\end{document}
