\documentclass[aspectration=1610]{beamer}

\usetheme{Hannover}
\usecolortheme{rose}
\definecolor{JagBlue}{HTML}{00205B}
\definecolor{JagRed}{HTML}{BF0D3E}

\usepackage{tikz,pgfplots}

%Center frame titles
\setbeamertemplate{frametitle}[default][center]

\title{Linear Algebra}

\date{Spring 2020}


\begin{document}



\begin{frame}\frametitle{Interpreting Feedback}
On each assessment, for each standard you will receive one of the following marks.
\begin{itemize}
\item {\bf M} means you demonstrated \textbf{Mastery} of that standard.
      Great job!  Check off another box on your progress sheet.
\item {\bf *} means you have a minor mistake, but if you can come by my office hours and explain it,
      this mark will be changed to {\bf M}.
\item {\bf W} means you have demonstrated understanding, but not written a complete solution.  Often, notation is poor or ambiguous.  You can provide a {\bf Written} re-working of the same problem (fixing any errors) to earn an {\bf M}.
\item {\bf R} means you made a good faith effort and demonstrated
      partial understanding, but not complete mastery. You are eligible to
      \textbf{Reattempt} the standard outside of class.
\item {\bf N} means there was \textbf{No Significant Evidence} of understanding.
\end{itemize}

\vspace{0.2in}

Marks other than M do not improve your course letter grade, but
they don't hurt you either.
\end{frame}

\begin{frame}\frametitle{Assessment Opportunities}
Checkmarks may be earned as follows.
\begin{itemize}
\item {\bf Quizzes}: Most weeks, one day at the end of class we will have a quiz. 
\item {\bf Exams}: Periodically we will have longer assessments (usually on Friday).
\item {\bf Final Exam}: Your final opportunity to demonstrate mastery,
      cumulative over the entire course.
\item {\bf Office Hours Reassessments}: A limited number of opportunities
      will be provided to earn checkmarks outside of class.
\end{itemize}

\pause

\vspace{0.2in}

The assessment method (quiz/exam/etc.) you used to earn a checkmark
isn't important: \textbf{I only care that you
learn the material and demonstrate that mastery to me before the end of the
semester!}
\end{frame}




\begin{frame}\frametitle{Course Grades}

\begin{center}
\begin{tabular}{ll} \hline
A & Earn 45 mastery checkmarks.\\ \hline
B & Earn 40 mastery checkmarks. \\ \hline
C & Earn 35 mastery checkmarks.\\ \hline
D & Earn 30 mastery checkmarks. \\ \hline
\end{tabular}
\end{center}

\end{frame}



\end{document}
