\documentclass{article}

\usepackage[margin=1in]{geometry}

\pagestyle{empty}

\begin{document}

\begin{center}
\textbf{Math 237 \\ Final}
\end{center}

This is completely optional. If you do not complete it, I will compute your course grade based on the number of standards you demonstrated mastery of, as described in the syllabus. If you complete this, I will determine your course grade by considering the number of standards you mastered; how thorough, detailed, and thoughtful your responses are here; and my professional judgement.

\begin{enumerate}
\item \textbf{What mathematical ideas are you curious to know more about as a result of taking this class?}  Give one example of a question about the material that you'd like to explore further, and describe why this is an interesting question to you.

\item \textbf{Take one of the topics we have studied, and explain how it can be applied to your field of study.}  Provide details of how you will use this in your future endeavors. What other problems will you be able to solve with the tools you have learned in this class? Give as many examples as you can. This will probably require you to do a bit of research!

\item \textbf{Take one standard you have worked on this semester that you struggled to fully understand, and explain how the struggle itself was valuable.}  In the context of this question, describe the struggle and how you overcame the struggle. You might also discuss whether struggling built aspects of character in you (e.g. endurance, self-confidence, competence to solve new problems) and how these virtues might benefit you in later ventures.

\item \textbf{One of the stated course objectives is for you to be able to work collaboratively on difficult mathematics problems. Discuss how you have improved in your ability to do so over the course of the semester.} You might wish to describe particular problems you worked on, or particularly memorable moments of collaboration with your teammates, either inside or outside of class. 

\item \textbf{Pretend there were no guidelines in the syllabus for calculating your final grade. Based on the work you have done all semester and the stated goals for the course, what grade do you think you have earned?} Learning is not always measured accurately by quizzes and exams. What other evidence of your learning is there? This could include the number of assignments completed (e.g. weekly discussions and self assessments), a description of your participation in class (both within your group and with the whole class), your final self assessment of your understanding of the content, and/or additional evidence of your understanding of particular topics that may not have been adequately captured on assessments. Use this space to share anything that will help me more accurately assign a course grade that reflects how much you have learned in this course.
\end{enumerate}
\end{document}
