\documentclass[letterpaper]{article}

\usepackage[top=0.25in,bottom=0.5in,left=0.75in,right=0.75in]{geometry}
\usepackage{enumerate,hyperref,amssymb,multicol}
\usepackage{array}


\input{../course-specific-macros.tex}

\newcommand{\boxes}{\(\Box\) \(\Box\)}


\pagestyle{empty}
\begin{document}

 Date: \underline{\phantom{xxxxxxxxxxxxxxxxx}} \hfill
  Name: \underline{\phantom{xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx}}\\

\begin{center}
{\Large \bf Self Assessment} \\
%\large \course
\end{center}
	
%\vspace{0.2in}

For each standard, record how many mastery checkmarks have you earned on assessments so far.  Then, rate your progress on mastering the standard on the following scale:
\begin{multicols}{2}
\begin{enumerate}[1.]
\item I need more time to understand this.
\item I can do this with the help of an example.
\item I can do this, but I still make errors sometimes.
\item I can do this and explain my solution to others.
\end{enumerate}
\end{multicols}


%\newlength{\extrarowheight}
\setlength{\extrarowheight}{9pt}

\hfill
\begin{tabular}{|c|c|c|} \hline
Standard & Mastery & Progress \\ \hline
E1 & \boxes &   \\  \hline
E2 & \boxes &   \\  \hline
E3 & \boxes &   \\  \hline
V1 & \boxes &   \\  \hline
V2 & \boxes &   \\  \hline
V3 & \boxes &  \\  \hline
V4 & \boxes & \\  \hline
V5 & \boxes &  \\  \hline
V6 & \boxes &  \\  \hline
V7 & \boxes &  \\  \hline
V8 & \boxes &  \\  \hline
V9 & \boxes &  \\  \hline
%
%\end{tabular}
%\hfill
%\begin{tabular}{|c|c|c|} \hline
%Standard & Mastery & Progress \\ \hline
V10 & \boxes & \\  \hline
A1& \boxes & \\  \hline
A2 & \boxes &  \\  \hline
A3 & \boxes &  \\  \hline
A4 & \boxes &  \\  \hline
M1 & \boxes &  \\  \hline
M2 & \boxes &  \\  \hline
M3 & \boxes &  \\  \hline
G1 & \boxes &  \\  \hline
G2 & \boxes &  \\  \hline
G3 & \boxes &  \\  \hline
G4 & \boxes &  \\  \hline
\end{tabular}
\hfill
\hfill

\ \\

\vspace{0.1in}

Answer the questions on the back.

\newpage
\ \\

\vspace{0.2in}

\begin{enumerate}
\setlength{\itemsep}{1.6in}
\item Which standard is most challenging for you so far? Why?
\item Which standard have you practiced the most so far? Why?
\item What grade do you hope to earn in this class? How many checkmarks do you need to earn that grade?
\item What do you need to do to achieve that grade?
\item Do you have any questions or thoughts you would like to share about your progress in this class so far?
\end{enumerate}
  
\end{document}